Estimation of Intracortical Connectivity in a Dynamical Neural Field Model

### 2010-06-24 ltx/PLoS/LaTeX_Manuscript.tex
small edits to paper

The sensors were spaced on a regular square $14 \times 14$ grid, the sensor width was set to $\sigma^2_m = 0.81$. This provides a width of $1.5$~mm at half the maximum amplitude of the basis function, with spacing $\Delta_y = 1.5$~mm. This arrangement modelled the recording as having some cross talk, which is typical for neurophysiological recordings.
     		\includegraphics{./Graph/ExperimentalFigure.pdf}
    	\caption{{\bf Example of the spatio-temporal properties of the model and synthetically generated data.} \textbf{(A)} Example of the neural field at a single time instant. (\textbf{B}) Example of data generated by the full neural field model from the first 5 sensors. (\textbf{C}) Power spectral density of the data generated by an observation showing the typical $1/f^2$ characteristic of intracranial EEG.} 
 \label{fig:experimental design}
\subsection*{Spatial Frequency Analysis} 
Using the model selection techniques described in Section~\ref{SpectralAnalysisSection}, the spatial frequency analysis was used to confirm that the spacing and width of the sensors was adequate to capture the significant dynamics of the field. Figure~\ref{fig:FFTTrueEstimate}(A) shows the spatial frequency of the neural field. The cut-off frequency of the neural field is $\nu_c \approx 0.24$~Hz ($-3$~dB point). From equation~\ref{eq:MinimumSensorDistance}, this yielded a minimum sensor separation of $2.05$~mm. This confirms that the separation of $\Delta_{y} = 1.5$~mm was sufficient to prevent problems associated with spatial aliasing.
\centering
\label{fig:FieldFFT}\includegraphics{./Graph/FFTField.pdf}
\caption{{\bf Spatial frequency analysis of the neural field}. (\textbf{A}) The average (over time) power in dB of the spatial frequency of the neural field. (\textbf{B}) The average (over time) power in dB of the spatial frequency of the reconstructed neural field from the basis function decomposition. The reconstructed field shows a narrower bandwidth as a result of the band limiting properties of the sensors and basis functions.}
\label{fig:FFTTrueEstimate}
The spatial frequency of the observed field is shown in Figure~\ref{fig:ObservationFreqAnal}(C). The cut-off frequency is $\nu_{cy} \approx 0.2$~Hz ($-3$~dB point). The observation cut-off frequency is lower than the field cut-off due to the low-pass filtering effect of the sensors. The spatial frequency response of the sensors can be seen in Figure~\ref{fig:ObservationFreqAnal}(A). Using an oversampling parameter of $\rho_{\phi}=1$, the minimum distance between the field basis functions was calculated to be $2.5$~mm to satisfy Shannon's sampling criterion (from equation~\ref{eq:BasisFunctionSeparation}). The distance between basis functions was set to $\Delta_{\phi}=2.5$~mm, which is sufficient to capture the significant dynamics according to our criteria.
Given the basis function separation, the basis function width parameter was set to $\sigma_{\phi}^2=2.5$~mm. This allowed a smooth representation of the field by the basis function decomposition up to a spatial frequency $\mathbf{\nu_{c\phi}} \approx 0.12$~Hz, as described by equation~\ref{eq:CutoffFromBasisFuncWidth}. The band-limiting effect is due to the spatial frequency response of the basis functions as seen in Figure~\ref{fig:ObservationFreqAnal}(B). The spatial frequency of the reconstructed field from the basis function decomposition is shown in Figure~\ref{fig:FFTTrueEstimate}(B). This figure illustrates the band-limiting effect of the basis function decomposition.
\begin{figure}[!ht] 
		\includegraphics{./Graph/SensorBasisObsFrequencyResponse.pdf}	
	\caption{{\bf Spatial frequency analysis}. The dashed line shows the cut-off frequency (-3 dB point). (\textbf{A}) Two-dimensional spatial frequency in power dB, averaged over 400 time steps) of the observed field. The symmetry of the sensors and field basis functions allow for the one-dimensional representation of the spectral characteristics. (\textbf{B}) The spatial frequency response of a one-dimensional model sensor. (\textbf{C}) The spatial frequency response of a one-dimensional neural field basis function, illustrating a narrower band width than the sensors.} 
	\label{fig:ObservationFreqAnal}

@@

\begin{figure}
    \centering
% \subfigure[][]{
\includegraphics{./Graph/KernelEstimate.pdf}%}
\caption{{\bf Cross-section of connectivity kernel estimate}. The actual kernel is shown by the solid line, the mean kernel estimate (over 100 realisations) is shown by the dotted line and the $95~\%$ confidence interval is shown by the shaded grey region.}
\label{fig:KernelEstimates}
\end{figure}
The accuracy of the state estimates was evaluated by comparing the field reconstruction to the true field using the mean (over iterations) of the root mean square error (MRMSE) (over space). The MRMSE of the field estimates over time for 100 realisations is shown in Figure~\ref{fig:RMSE}, with the $95~\%$ confidence interval. At each time point the error is consistently around 0.5~mV, which is approximately $7.1$~\% of the field voltage range ($[-3.29,3.77]$~mV). The error in the reconstructed field is mostly due to the loss of high spatial frequency information from the basis function decomposition as illustrated in Figure~\ref{fig:FieldEstimate}. The figure shows a snapshot at a single time instant of the true neural field, the estimated field and the corresponding error, which is the difference between the true and estimated neural fields. It can be seen in Figure~\ref{fig:FieldEstimate}(B) that the estimated field contains the basic structure of the true field (Figure~\ref{fig:FieldEstimate}(A)), but is missing the higher-frequency detail.
  \begin{figure}
   	\begin{center}
   		\includegraphics{./Graph/MRMSE.pdf} 
   	\end{center}
   	\caption{{\bf The mean of average RMSE of the estimated field over 100 realisations (solid line) and the 95~\% confidence interval (grey region).}} 
\label{fig:RMSE}
   \end{figure}

@@

\begin{table}[!ht]
\caption{
\bf{Notation}}
\begin{tabular}{|c|l|l|}
	\hline
	\textbf{Symbol} & \textbf{Quantity} & \textbf{Units}\\
	\hline
	\multicolumn{3}{|c|}{\emph{Domain and indices}}\\
	\hline
	$\Omega$ & spatial domain & n.a.\\
	$\mathbf{r}$ & spatial location & [mm, mm]\\
	$t$ & time & s\\
	\hline
	\multicolumn{3}{|c|}{\emph{Model}}\\
	\hline
    $y(\mathbf{r}_n,t)$ & observation & mV\\
    $v(\mathbf{r},t)$ & mean membrane potential & mV \\
	$g(\mathbf{r},t)$ & weighted firing rate function & spikes.s$^{-1}$\\
	$f(\mathbf{r},t)$ & firing rate function & spikes.s$^{-1}$\\
	$e(\mathbf{r},t)$ & field disturbance, with covariance function $\gamma(\mathbf r-\mathbf r')$ & mV\\
	$\varepsilon(\mathbf{r}_n,t)$ & observation noise, with covariance matrix $\Sigma_\varepsilon$ & mV\\
	$m(\mathbf{r}_n,\mathbf{r}')$ & sensor kernel where $n$ is sensor index $n=1,..,N$ (width $\sigma_m^2$) & n.a. \\
	$w(\mathbf{r},\mathbf{r}')$ & spatial connectivity kernel & n.a.\\
	$h(t)$ & post-synaptic response kernel & mV\\
	$\zeta$ & inverse synaptic time constant & s$^{-1}$\\
	$\xi$ & time constant parameter & n.a.\\
	$\eta(t)$ & Heaviside step function & n.a.\\
	$\delta(t)$ & Dirac-delta function & n.a.\\
	$D$ & temporal differential operator & n.a.\\
	\hline
	\multicolumn{3}{|c|}{\emph{Reduced Model}} \\
	\hline
   	$\boldsymbol\phi(\mathbf{r})$ & vector of $L$ Gaussian basis functions & n.a.\\
   	$\mathbf{x}_t$ & state vector at time $t$ & mV\\
   	$\boldsymbol{\psi}(\mathbf{r}-\mathbf{r}')$ & vector of connectivity kernel basis functions & n.a.\\
   	$\Gamma$ & inner product of field basis functions & n.a.\\
   	$q()$ & parameterised nonlinear state function (used in LS estimator) & n.a.\\
   	$Q()$ & state transition function &\\
   	$\mathbf{e}_t$ & state disturbance vector, with covariance $\Sigma_e$ & mV\\
   	$\mathbf{C}$ & observation matrix & n.a. \\
	\hline
	\multicolumn{3}{|c|}{\emph{Frequency Analysis}} \\
	\hline
    $V(\nu)$ & Fourier transform of the neural field & Hz\\
	$\nu$ & Spatial frequency & Hz \\
	$\nu_c$ & Field spatial cut-off frequency & Hz\\
	$\sigma_{\nu}^2$ & Variance of Fourier transformed Gaussian basis function & Hz$^2$\\
	\hline
	\multicolumn{3}{|c|}{\emph{Estimation}} \\
	\hline
	$\mathcal{X}$ & matrix of sigma vectors & mV\\
	$W$ & matrix of sigma vector weights (scaling parameter $\lambda$) & n.a.\\
   	$\hat{\mathbf{x}}_t^{f-}$, $\hat{\mathbf{x}}_t^f$ & forward prior and posterior state estimates & mV\\
   	$\hat{\mathbf{x}}_t^{b-}$, $\hat{\mathbf{x}}_t^{b}$ & backward prior and posterior state estimates & mV\\
 	$P^{f-}_t$, $P^f_t$  & forward prior and posterior covariance matrices & mV$^2$\\
   	$P^{b-}_t$, $P^b_t$ & backward prior and posterior covariance matrices & mV$^2$\\
	$M_t$& cross-covariance matrix & mV$^2$\\
	$\mathcal K_{t} $ & filter gain & n.a.\\
	$S_t$ & smoother gain & n.a.\\	
	\hline
\end{tabular}
\begin{flushleft}The first column of the table gives the symbols for all the notation used the paper. The second column provides a brief description of the quantity, and the third column provide the relevant SI unit where appropriate.
\end{flushleft}
\label{tab:label}
\end{table}

\renewcommand{\arraystretch}{1.8}
\begin{table}[!ht]
\caption{
\bf{Steps in the Algorithm for the Unscented RTS Smoother}}
\begin{tabular}{|c|}\hline
\multicolumn{1}{|p{16cm}|}{\textbf{1.} Forward initialisation} \\ 
$\hat{\mathbf x}_0, \mathbf P_0$ \\
\hline
\multicolumn{1}{|p{16cm}|}{\textbf{2.} Forward iteration: for $t \in \left\lbrace 0,\cdots, T\right\rbrace $, calculate the sigma points $\mathcal X_{i,t}^f$ using equations \ref{eq:sigmapoints1}-\ref{eq:sigmapoints3} and propagate through equation~\ref{eq:QmatrixForSigmapoints}} \\
$\mathcal X_{i,t+1}^{f-}=Q(\mathcal X_{i,t}^f) \quad i=0, \dots, 2L$\\
\multicolumn{1}{|p{16cm}|}{Calculate the predicted state and the predicted covariance matrix} \\
$\hat{\mathbf x}_{t+1}^{f-}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,t+1}^{f-} $ \\
$\mathbf P_{t +1}^{f-}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})^\top+\boldsymbol \Sigma_e$ \\ 
\multicolumn{1}{|p{16cm}|}{Compute the filter gain, the filtered state and the filtered covariance matrix using the standard Kalman filter update equations} \\
$\mathcal K_{t+1}=\mathbf P_{t +1}^{f-}\mathbf C ^\top(\mathbf C \mathbf P_{t +1}^{f-}\mathbf C ^\top+\boldsymbol \Sigma_{\varepsilon})^{-1}$\\
$\hat{\mathbf x}_{t+1}^{f}=\hat{\mathbf x}_{t+1}^{f-}+\mathcal K_{t+1}(\mathbf y_{t+1}-\mathbf C\hat{\mathbf x}_{t +1}^{f-}) $\\
$\mathbf P_{t+1}^f=(\mathbf I - \mathcal K_{t+1}\mathbf C)\mathbf P_{t +1}^{f-}$\\ 
\hline
\multicolumn{1}{|p{16cm}|}{\textbf{3.} Backward initialisation}\\
$\mathbf P_T^b= \mathbf P_T^f, \quad \hat{\mathbf x}^b_T= \hat{\mathbf x}^f_T$ \\
\hline
\multicolumn{1}{|p{16cm}|}{\textbf{4.} Backward iteration: for $t \in \left\lbrace T-1, \cdots, 0 \right\rbrace $ calculate the sigma points $\mathcal X_{i,t}^b$ and propagate them through equation \ref{eq:QmatrixForSigmapoints}}\\
$\mathcal X_{i,t+1}^{b-}=Q(\mathcal X_{i,t}^b) \quad i=0, \dots, 2L$\\
\multicolumn{1}{|p{16cm}|}{Calculate the predicted state and the predicted covariance matrix}\\
$\hat{\mathbf x}_{t+1}^{b-}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,t+1}^{b-}$\\
$\mathbf P_{t +1}^{f-}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})^\top+\boldsymbol \Sigma_e $\\
$\mathbf M_{t +1}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t}^{b-}-\hat{\mathbf x}_{t}^{f})(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t+1}^{b-})^\top$\\
\multicolumn{1}{|p{16cm}|}{Compute the smoother gain, the smoothed state and the smoothed covariance matrix}\\
$\mathbf S_t=\mathbf M_{t +1}\left[ \mathbf P_{t +1}^{b-}\right] ^{-1} $\\
$\hat{\mathbf x}_t^b=\hat{\mathbf x}_t^f+\mathbf S_t\left[\hat{\mathbf x}_{t+1}^{b}-\hat{\mathbf x}_{t+1}^{b-}\right]$\\
$\mathbf P_{t}^{b}=\mathbf P_{t}^{f}+\mathbf S_t\left[\mathbf P_{t+1}^{b}-\mathbf P_{t+1}^{b-} \right]\mathbf S_t^\top $\\
\hline
\end{tabular}
\begin{flushleft}This table shows the steps in the unscented Rauch-Tung-Striebel smoother algorithm. The steps are iterated 11 times for our state estimation procedure. The least squares algorithm is run after each iteration to update the parameter estimates.
\end{flushleft}
\label{tab:UKFAlgorithm}
\end{table}

>>>>

The sensors were spaced on a regular square $14 \times 14$ grid, the sensor width was set to $\sigma^2_m = 0.81$. This provides a width of $1.5$~mm at half the maximum amplitude of the basis function, with spacing $\Delta_y = 1.5$~mm. This arrangement modelled the recording as having some cross talk, which is typical for neurophysiological recordings.
 \begin{figure}
    	\begin{center}
     		\includegraphics{./Graph/ExperimentalFigure.pdf}
    	\end{center}
    	\caption{{\bf Example of the spatio-temporal properties of the model and synthetically generated data.} \textbf{(A)} Example of the neural field at a single time instant. (\textbf{B}) Example of data generated by the full neural field model from the first 5 sensors. (\textbf{C}) Power spectral density of the data generated by an observation showing the typical $1/f^2$ characteristic of intracranial EEG.} 
 \label{fig:experimental design}
 \end{figure}
\subsection*{Spatial Frequency Analysis} 
Using the model selection techniques described in Section~\ref{SpectralAnalysisSection}, the spatial frequency analysis was used to confirm that the spacing and width of the sensors was adequate to capture the significant dynamics of the field. Figure~\ref{fig:FFTTrueEstimate}(A) shows the spatial frequency of the neural field. The cut-off frequency of the neural field is $\nu_c \approx 0.24$~Hz ($-3$~dB point). From equation~\ref{eq:MinimumSensorDistance}, this yielded a minimum sensor separation of $2.05$~mm. This confirms that the separation of $\Delta_{y} = 1.5$~mm was sufficient to prevent problems associated with spatial aliasing.
\begin{figure}
\centering
\label{fig:FieldFFT}\includegraphics{./Graph/FFTField.pdf}
\caption{{\bf Spatial frequency analysis of the neural field}. (\textbf{A}) The average (over time) power in dB of the spatial frequency of the neural field. (\textbf{B}) The average (over time) power in dB of the spatial frequency of the reconstructed neural field from the basis function decomposition. The reconstructed field shows a narrower bandwidth as a result of the band limiting properties of the sensors and basis functions.}
\label{fig:FFTTrueEstimate}
\end{figure}

The spatial frequency of the observed field is shown in Figure~\ref{fig:ObservationFreqAnal}(C). The cut-off frequency is $\nu_{cy} \approx 0.2$~Hz ($-3$~dB point). The observation cut-off frequency is lower than the field cut-off due to the low-pass filtering effect of the sensors. The spatial frequency response of the sensors can be seen in Figure~\ref{fig:ObservationFreqAnal}(A). Using an oversampling parameter of $\rho_{\phi}=1$, the minimum distance between the field basis functions was calculated to be $2.5$~mm to satisfy Shannon's sampling criterion (from equation~\ref{eq:BasisFunctionSeparation}). The distance between basis functions was set to $\Delta_{\phi}=2.5$~mm, which is sufficient to capture the significant dynamics according to our criteria.
Given the basis function separation, the basis function width parameter was set to $\sigma_{\phi}^2=2.5$~mm. This allowed a smooth representation of the field by the basis function decomposition up to a spatial frequency $\mathbf{\nu_{c\phi}} \approx 0.12$~Hz, as described by equation~\ref{eq:CutoffFromBasisFuncWidth}. The band-limiting effect is due to the spatial frequency response of the basis functions as seen in Figure~\ref{fig:ObservationFreqAnal}(B). The spatial frequency of the reconstructed field from the basis function decomposition is shown in Figure~\ref{fig:FFTTrueEstimate}(B). This figure illustrates the band-limiting effect of the basis function decomposition.
\begin{figure}[!ht] 
	\begin{center}
		\includegraphics{./Graph/SensorBasisObsFrequencyResponse.pdf}	
	\end{center}
	\caption{{\bf Spatial frequency analysis}. The dashed line shows the cut-off frequency (-3 dB point). (\textbf{A}) Two-dimensional spatial frequency in power dB, averaged over 400 time steps) of the observed field. The symmetry of the sensors and field basis functions allow for the one-dimensional representation of the spectral characteristics. (\textbf{B}) The spatial frequency response of a one-dimensional model sensor. (\textbf{C}) The spatial frequency response of a one-dimensional neural field basis function, illustrating a narrower band width than the sensors.} 
	\label{fig:ObservationFreqAnal}
\end{figure}

@@

\begin{figure}
    \centering
% \subfigure[][]{
\includegraphics{./Graph/KernelEstimate.pdf}%}
\caption{{\bf Cross-section of connectivity kernel estimate}. The actual kernel is shown by the solid line, the mean kernel estimate (over 100 realisations) is shown by the dotted line and the $95~\%$ confidence interval is shown by the shaded grey region.}
\label{fig:KernelEstimates}
\end{figure}
The accuracy of the state estimates was evaluated by comparing the field reconstruction to the true field using the mean (over iterations) of the root mean square error (MRMSE) (over space). The MRMSE of the field estimates over time for 100 realisations is shown in Figure~\ref{fig:RMSE}, with the $95~\%$ confidence interval. At each time point the error is consistently around 0.5~mV, which is approximately $7.1$~\% of the field voltage range ($[-3.29,3.77]$~mV). The error in the reconstructed field is mostly due to the loss of high spatial frequency information from the basis function decomposition as illustrated in Figure~\ref{fig:FieldEstimate}. The figure shows a snapshot at a single time instant of the true neural field, the estimated field and the corresponding error, which is the difference between the true and estimated neural fields. It can be seen in Figure~\ref{fig:FieldEstimate}(B) that the estimated field contains the basic structure of the true field (Figure~\ref{fig:FieldEstimate}(A)), but is missing the higher-frequency detail.
  \begin{figure}
   	\begin{center}
   		\includegraphics{./Graph/MRMSE.pdf} 
   	\end{center}
   	\caption{{\bf Error in the field reconstruction}. The mean of average RMSE of the estimated field over 100 realisations (solid line) and the 95~\% confidence interval (grey region).} 
\label{fig:RMSE}
   \end{figure}

@@

\begin{table}[!ht]
\caption{
\bf{Notation}}
\begin{tabular}{|l|l|l|}
	\hline
	\textbf{Symbol} & \textbf{Quantity} & \textbf{Units}\\
	\hline
	\multicolumn{3}{|c|}{\emph{Domain and indices}}\\
	\hline
	$\Omega$ & spatial domain & n.a.\\
	$\mathbf{r}$ & spatial location & [mm, mm]\\
	$t$ & time & s\\
	\hline
	\multicolumn{3}{|c|}{\emph{Model}}\\
	\hline
    $y(\mathbf{r}_n,t)$ & observation & mV\\
    $v(\mathbf{r},t)$ & mean membrane potential & mV \\
	$g(\mathbf{r},t)$ & weighted firing rate function & spikes.s$^{-1}$\\
	$f(\mathbf{r},t)$ & firing rate function & spikes.s$^{-1}$\\
	$e(\mathbf{r},t)$ & field disturbance, with covariance function $\gamma(\mathbf r-\mathbf r')$ & mV\\
	$\varepsilon(\mathbf{r}_n,t)$ & observation noise, with covariance matrix $\Sigma_\varepsilon$ & mV\\
	$m(\mathbf{r}_n,\mathbf{r}')$ & sensor kernel where $n$ is sensor index $n=1,..,N$ (width $\sigma_m^2$) & n.a. \\
	$w(\mathbf{r},\mathbf{r}')$ & spatial connectivity kernel & n.a.\\
	$h(t)$ & post-synaptic response kernel & mV\\
	$\zeta$ & inverse synaptic time constant & s$^{-1}$\\
	$\xi$ & time constant parameter & n.a.\\
	$\eta(t)$ & Heaviside step function & n.a.\\
	$\delta(t)$ & Dirac-delta function & n.a.\\
	$D$ & temporal differential operator & n.a.\\
	\hline
	\multicolumn{3}{|c|}{\emph{Reduced Model}} \\
	\hline
   	$\boldsymbol\phi(\mathbf{r})$ & vector of $L$ Gaussian basis functions & n.a.\\
   	$\mathbf{x}_t$ & state vector at time $t$ & mV\\
   	$\boldsymbol{\psi}(\mathbf{r}-\mathbf{r}')$ & vector of connectivity kernel basis functions & n.a.\\
   	$\Gamma$ & inner product of field basis functions & n.a.\\
   	$q()$ & parameterised nonlinear state function (used in LS estimator) & n.a.\\
   	$Q()$ & state transition function &\\
   	$\mathbf{e}_t$ & state disturbance vector, with covariance $\Sigma_e$ & mV\\
   	$\mathbf{C}$ & observation matrix & n.a. \\
	\hline
	\multicolumn{3}{|c|}{\emph{Frequency Analysis}} \\
	\hline
    % $V(\nu)$ & Fourier transform of the neural field & Hz\\
	$\nu$ & Spatial frequency & Hz \\
	$\nu_c$ & Field spatial cut-off frequency & Hz\\
	$\sigma_{\nu}^2$ & Variance of Fourier transformed Gaussian basis function & Hz$^2$\\
	\hline
	\multicolumn{3}{|c|}{\emph{Estimation}} \\
	\hline
	$\mathcal{X}$ & matrix of sigma vectors & mV\\
	$W$ & matrix of sigma vector weights (scaling parameter $\lambda$) & n.a.\\
   	$\hat{\mathbf{x}}_t^{f-}$, $\hat{\mathbf{x}}_t^f$ & forward prior and posterior state estimates & mV\\
   	$\hat{\mathbf{x}}_t^{b-}$, $\hat{\mathbf{x}}_t^{b}$ & backward prior and posterior state estimates & mV\\
 	$P^{f-}_t$, $P^f_t$  & forward prior and posterior covariance matrices & mV$^2$\\
   	$P^{b-}_t$, $P^b_t$ & backward prior and posterior covariance matrices & mV$^2$\\
	$M_t$& cross-covariance matrix & mV$^2$\\
	$\mathcal K_{t} $ & filter gain & n.a.\\
	$S_t$ & smoother gain & n.a.\\	
	\hline
\end{tabular}
\begin{flushleft}The first column of the table gives the symbols for all the notation used the paper. The second column provides a brief description of the quantity, and the third column provide the relevant SI unit where appropriate.
\end{flushleft}
\label{tab:label}
\end{table}

\renewcommand{\arraystretch}{1.7}
\begin{table}[!ht]
\caption{
\bf{Steps in the Algorithm for the Unscented RTS Smoother}}
\begin{tabular}{|c|}\hline
\multicolumn{1}{|p{16cm}|}{\textbf{1.} Forward initialisation} \\ 
$\hat{\mathbf x}_0, \mathbf P_0$ \\
\hline
\multicolumn{1}{|p{16cm}|}{\textbf{2.} Forward iteration: for $t \in \left\lbrace 0,\cdots, T\right\rbrace $, calculate the sigma points $\mathcal X_{i,t}^f$ using equations \ref{eq:sigmapoints1}-\ref{eq:sigmapoints3} and propagate through equation~\ref{eq:QmatrixForSigmapoints}} \\
$\mathcal X_{i,t+1}^{f-}=Q(\mathcal X_{i,t}^f) \quad i=0, \dots, 2L$\\
\multicolumn{1}{|p{16cm}|}{Calculate the predicted state and the predicted covariance matrix} \\
$\hat{\mathbf x}_{t+1}^{f-}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,t+1}^{f-} $ \\
$\mathbf P_{t +1}^{f-}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})^\top+\boldsymbol \Sigma_e$ \\ 
\multicolumn{1}{|p{16cm}|}{Compute the filter gain, the filtered state and the filtered covariance matrix using the standard Kalman filter update equations} \\
$\mathcal K_{t+1}=\mathbf P_{t +1}^{f-}\mathbf C ^\top(\mathbf C \mathbf P_{t +1}^{f-}\mathbf C ^\top+\boldsymbol \Sigma_{\varepsilon})^{-1}$\\
$\hat{\mathbf x}_{t+1}^{f}=\hat{\mathbf x}_{t+1}^{f-}+\mathcal K_{t+1}(\mathbf y_{t+1}-\mathbf C\hat{\mathbf x}_{t +1}^{f-}) $\\
$\mathbf P_{t+1}^f=(\mathbf I - \mathcal K_{t+1}\mathbf C)\mathbf P_{t +1}^{f-}$\\ 
\hline
\multicolumn{1}{|p{16cm}|}{\textbf{3.} Backward initialisation}\\
$\mathbf P_T^b= \mathbf P_T^f, \quad \hat{\mathbf x}^b_T= \hat{\mathbf x}^f_T$ \\
\hline
\multicolumn{1}{|p{16cm}|}{\textbf{4.} Backward iteration: for $t \in \left\lbrace T-1, \cdots, 0 \right\rbrace $ calculate the sigma points $\mathcal X_{i,t}^b$ and propagate them through equation \ref{eq:QmatrixForSigmapoints}}\\
$\mathcal X_{i,t+1}^{b-}=Q(\mathcal X_{i,t}^b) \quad i=0, \dots, 2L$\\
\multicolumn{1}{|p{16cm}|}{Calculate the predicted state and the predicted covariance matrix}\\
$\hat{\mathbf x}_{t+1}^{b-}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,t+1}^{b-}$\\
$\mathbf P_{t +1}^{f-}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})^\top+\boldsymbol \Sigma_e $\\
$\mathbf M_{t +1}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t}^{b-}-\hat{\mathbf x}_{t}^{f})(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t+1}^{b-})^\top$\\
\multicolumn{1}{|p{16cm}|}{Compute the smoother gain, the smoothed state and the smoothed covariance matrix}\\
$\mathbf S_t=\mathbf M_{t +1}\left[ \mathbf P_{t +1}^{b-}\right] ^{-1} $\\
$\hat{\mathbf x}_t^b=\hat{\mathbf x}_t^f+\mathbf S_t\left[\hat{\mathbf x}_{t+1}^{b}-\hat{\mathbf x}_{t+1}^{b-}\right]$\\
$\mathbf P_{t}^{b}=\mathbf P_{t}^{f}+\mathbf S_t\left[\mathbf P_{t+1}^{b}-\mathbf P_{t+1}^{b-} \right]\mathbf S_t^\top $\\
\hline
\end{tabular}
\begin{flushleft}This table shows the steps in the unscented Rauch-Tung-Striebel smoother algorithm. The steps are iterated 11 times for our state estimation procedure. The least squares algorithm is run after each iteration to update the parameter estimates.
\end{flushleft}
\label{tab:UKFAlgorithm}
\end{table}
